Post-doc project: A complex food-web theory of stability against perturbation

### 2023-01-12 report/project_definition.Rmd
Add module

```{r}
png(here("report", "figures", "spe_top_spe.png"),
  width = 480 * 1.618, height = 480, units = "px", bg = "transparent")
par(mfrow = c(1, 2))
PlotWeb(
  NetIndices::TrophInd(t(top_spe))$TL,
  t(top_spe),
  abund = rep(1, nrow(top_spe)), scale_abun = .3, colnode = "red")
title("Top generalist")
PlotWeb(
  NetIndices::TrophInd(t(spe))$TL,
  t(spe),
  abund = rep(1, nrow(spe)), scale_abun = .3, colnode = "green")
title("Specialist")
dev.off()
```

```{r}
gen_stab <- read_csv(here("generalism_stoch.csv"))

gen_stab %>%
  select(1:5) %>%
  mutate(
    stab_com = 1 / cv_com,
    fw = repl_module[fw]
    ) %>%
  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
    names_to = "metric", values_to = "values") %>%
  ggplot(aes(x = fw, y = values)) +
  geom_boxplot()  +
  facet_wrap(~metric, scales = "free_y")
```

>>>>

```{r}
png(here("report", "figures", "spe_top_spe.png"),
  width = 480 * 1.618, height = 480, units = "px", bg = "transparent")
par(mfrow = c(1, 2))
PlotWeb(
  NetIndices::TrophInd(t(top_spe))$TL,
  t(top_spe),
  abund = rep(1, nrow(top_spe)), scale_abun = .3, colnode = "red")
title("Top generalist")
PlotWeb(
  NetIndices::TrophInd(t(spe))$TL,
  t(spe),
  abund = rep(1, nrow(spe)), scale_abun = .3, colnode = "green")
title("Specialist")
dev.off()
```
```{r, out.height = "80%"}
knitr::include_graphics(here("report", "figures", "spe_top_spe.png"))
```

```{r, fig.height = 10}
gen_stab <- read_csv(here("generalism_stoch.csv"))

gen_stab %>%
  select(1:5) %>%
  mutate(
    stab_com = 1 / cv_com,
    fw = repl_module[fw]
    ) %>%
  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
    names_to = "metric", values_to = "values") %>%
  ggplot(aes(x = fw, y = values)) +
  geom_boxplot()  +
  facet_wrap(~metric, scales = "free_y", ncol = 1)
```
